Memory-Efficient Mixed-Precision Implementations\\for Robust Explicit Model Predictive Control

### 2019-04-12 emsoft-2019/Motiv.tex
updating sec. 2

% !TEX root = main.tex
\section{Overview}
\label{sec:example}

@@

\begin{figure}[t]
	\begin{tabular}{cc}
	\includegraphics[width=2cm,height=3cm]{Figs/inv_pend.png}&	\includegraphics[width=6cm,height=4cm]{Figs/regs.jpg}\\
	(a)&(b)
	\end{tabular}
	\caption{(a) Inverted pendulum; (b) 2-D plot of polyhedral partitions for an explicit MPC applied to the inverted pendulum.}
	\label{fig:inverted_pendulum}
\end{figure}

@@

Unfortunately, $\Delta_0=0.01$ is not realizable, as the point location error is $0.019$ and hence $e>\Delta_0$. 
%always greater than zero either due to selecting the wrong region in the affine controller function or due to the finite-precision computation of the control action.
%\eva{Is this the error due to mixed-precision or due to wrong regions?}
Therefore, we define $\Delta_1 := \Delta_0 + \varepsilon_{SAFE}$ with $\varepsilon_{SAFE}$ being a fixed threshold (we chose $\varepsilon_{SAFE} = 0.04$) and enlarge the disturbance set as $\mathcal W_{\Delta_1}$. 
Solving the robust explicit MPC problem for this enlarged disturbance set gives the new controller,
shown in Figure~\ref{fig:inverted_pendulum}(b).
The controller has $14$ regions.
\RM{give the control function. I think it will be good to explicitly write the polyhedra and the affine maps}

@@

\begin{figure}
\tikzstyle{block} = [draw, rectangle, minimum height=4em, minimum width=6em]
\tikzstyle{block1} = [draw, rectangle, minimum height=2em, minimum width=6em]
\tikzstyle{block2} = [draw, rectangle, minimum height=1em, minimum width=4em]
\tikzstyle{block3} = [draw, rectangle, minimum height=3.2em, minimum width=4em]
\tikzstyle{sum} = [draw,  circle, node distance=1cm]
\tikzstyle{input} = [coordinate]
\tikzstyle{output} = [coordinate]
\tikzstyle{pinstyle} = [pin edge={to-,thin,black}]

\centering
	\begin{tikzpicture}[auto,node distance=2cm,>=latex',scale=1]
	\node [block,scale=1,text width=3.8cm, pin={[pinstyle]above:$\Delta=\Delta_0$},
	node distance=1cm, align=center, label={[anchor=south east, draw=black, inner sep=1pt]south east:MATLAB}] (RMPC) {Robust explicit MPC\\with disturbance set $\mathcal W_{\Delta}$};
	%\node[] (partitions) at (2.5,.5){\includegraphics[width=.08\textwidth]{Figs/regs.jpg}};
	\node [block3, scale=1,below=1.3cm of RMPC,
	node distance=3.8cm,text width=4.4cm,  label={[anchor=south east, draw=black, inner sep=1pt]south east:Daisy}] (Uij) {Point location error computation};
	\node [draw, diamond, minimum height=3em, minimum width=3em, below =0.8cm of Uij, node distance=5cm] (decide) {$e\leq  \Delta$};
	\node [block3, below=0.8cm of decide,node distance=3cm, label={[anchor=south east, draw=black, inner sep=1pt]south east:Daisy}] (done) {Mixed-precision implementation};
	\node [block2, right=1.3cm of decide,
	node distance=3cm] (delta) {Increase $\Delta$};
	\node [block1,below = 0.8cm of done] (output) {Low-precision controller};
	%\node [scale=1] at (3,-.25)  {$u(x)=Kx+v$};
	\node at (9,-.25) {$e$};

	\draw [draw,->, align=center] (RMPC) -- node [left] {high-precision\\ controller}(Uij);
	\draw [->] (Uij) -- node [left] {$e$}(decide);
	\draw [->] (decide) -- node [left,pos=.3] {Yes} (done);
	\draw [->] (decide) -- node[pos=0.99] {} 
	node [] {No} (delta);
	\draw [->] (delta) |- node [above] {} (RMPC);
	\draw [->] (done) -- node [above] {} (output);

	%\node [block2, scale=0.7] at (1.3,-.42) {MATLAB} ;
	%\node [block2, scale=0.7] at (1.65,-2.95) {Daisy} ;
	%\node [block2, scale=0.7] at (1.58,-7) {Daisy} ;
	\end{tikzpicture}
	%\end{adjustbox}
	\caption{High-level description of the proposed memory-efficient robust MPC design.}
	\label{fig:overview}
\end{figure}

>>>>

% !TEX root = main.tex
\section{Overview}
\label{sec:example}
\begin{figure}
	\tikzstyle{block} = [draw, rectangle, minimum height=4em, minimum width=6em]
	\tikzstyle{block1} = [draw, rectangle, minimum height=2em, minimum width=6em]
	\tikzstyle{block2} = [draw, rectangle, minimum height=1em, minimum width=4em]
	\tikzstyle{block3} = [draw, rectangle, minimum height=3.2em, minimum width=4em]
	\tikzstyle{input} = [coordinate]
	\tikzstyle{output} = [coordinate]
	\tikzstyle{pinstyle} = [pin edge={to-,thin,black}]
	{\centering

		%\begin{center}
		%\hspace*{\fill} 
		\begin{tikzpicture}[auto,node distance=1cm,>=latex']
		\node [block,text width=3.8cm, pin={[pinstyle]above:$\Delta=\Delta_0$},
		node distance=1cm, align=center, label={[anchor=south east, draw=black, inner sep=1pt]south east:MATLAB}] (RMPC) {Robust explicit MPC\\with disturbance set $\mathcal W_{\Delta}$};
		%\node[] (partitions) at (2.5,.5){\includegraphics[width=.08\textwidth]{Figs/regs.jpg}};
		\node [block3,below=1.3cm of RMPC,
		node distance=1cm,text width=4.4cm,  label={[anchor=south east, draw=black, inner sep=1pt]south east:MATLAB}] (Uij) {Incorrect region selection error};
		\node [draw, diamond, minimum height=3em, minimum width=3em, below =0.8cm of Uij, node distance=1cm] (decide) {$e\leq  \Delta$};
		\node [block3, below=0.8cm of decide,node distance=1cm, label={[anchor=south east, draw=black, inner sep=1pt]south east:Daisy}] (done) {Mixed-precision implementation};
		\node [block2, right=1.3cm of decide,
		node distance=1cm] (delta) {Increase $\Delta$};
		\node [block1,below = 0.8cm of done] (output) {Low-precision controller};
		%\node [scale=1] at (3,-.25)  {$u(x)=Kx+v$};
		\node at (9,-.25) {$e$};

		\draw [draw,->, align=center] (RMPC) -- node [left] {high-precision\\ controller}(Uij);
		\draw [->] (Uij) -- node [left] {$e$}(decide);
		\draw [->] (decide) -- node [left,pos=.3] {Yes} (done);
		\draw [->] (decide) -- node[pos=0.99] {} 
		node [] {No} (delta);
		\draw [->] (delta) |- node [above] {} (RMPC);
		\draw [->] (done) -- node [above] {} (output);
		%\node [block2, scale=0.7] at (1.3,-.42) {MATLAB} ;
		%\node [block2, scale=0.7] at (1.65,-2.95) {Daisy} ;
		%\node [block2, scale=0.7] at (1.58,-7) {Daisy} ;
		\end{tikzpicture}\par}
	%	\hspace{\fill} 
	%\end{center}
	%\end{adjustbox}
	\caption{High-level description of the proposed memory-efficient robust MPC design.}
	\label{fig:overview}
\end{figure}

@@

\begin{figure}[h]
	\begin{tabular}{cc}
	\includegraphics[width=2cm,height=3cm]{Figs/inv_pend.png}&	\includegraphics[width=6cm,height=4cm]{Figs/regs.jpg}\\
	(a)&(b)
	\end{tabular}
	\caption{(a) Inverted pendulum; (b) 2-D plot of polyhedral partitions for an explicit MPC applied to the inverted pendulum.}
	\label{fig:inverted_pendulum}
\end{figure}

@@

Unfortunately, $\Delta_0=0.01$ is not realizable, as the point location error is $0.019$ and hence $e>\Delta_0$. 
%always greater than zero either due to selecting the wrong region in the affine controller function or due to the finite-precision computation of the control action.
%\eva{Is this the error due to mixed-precision or due to wrong regions?}
Therefore, we define $\Delta_1 := \Delta_0 + \varepsilon_{SAFE}$ with $\varepsilon_{SAFE}$ being a fixed threshold (we chose $\varepsilon_{SAFE} = 0.04$) and enlarge the disturbance set as $\mathcal W_{\Delta_1}$. 
Solving the robust explicit MPC problem for this enlarged disturbance set gives the new controller,
shown in Figure~\ref{fig:inverted_pendulum}(b).
The controller has $14$ regions. Following demostrates one sample mapping, including the activation condition and its corresponding affine function
\begin{equation*}
\resizebox{.9\hsize}{!}{$
\begin{bmatrix}
-0.005  &0.999\\
-0.998  &-0.049\\
0.005  &-0.999\\
0.998   &0.049
\end{bmatrix}x_k\leq 
\begin{bmatrix}
0.416\\
3.157\\
0.617\\
-0.0124
\end{bmatrix}
\Rightarrow
u(x_k)=\begin{bmatrix}
0.05&-9.67
\end{bmatrix}x_k+4.02$}
\end{equation*}
where, output of robust EMPC at state $x_k$ is denoted by $u(x_k)$. Notice that all the rest of mappings have similar format.
%\RM{give the control function. I think it will be good to explicitly write the polyhedra and the affine maps}

@@
